Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-07 appendix.tex
tex

~\newline
\noindent\textbf{II. Complete Experimental Results for Tab.~2 in Manuscript}

They can be found in \cref{tab:srcdest} of this supplementary material.

\hrule

	[\xmark] Multicard DDP and single card training leads to different
		performance, regardless of the exact model of GPUs.
		%
		According to the observation, single card training leadss to a lower
		recall performance and a higher robustness score.
		%
		More efficient? This should be ok.
		%
		But be careful when doing ablation studies as this will greatly
		interfere with the conclusions.

@@

>>>>

For reference, the adversarial training cost of RN18 with two Nvidia Titan Xp
GPUs in terms of wall time is summarized in
%
\oo{todo}

~\newline
\noindent\textbf{II. Complete Results for Tab.~2 in Manuscript}

Complete experimental results for ``Tab.~2: Combinations of Source \&
Destination Hardness. \ldots'' can be found in \cref{tab:srcdest} of this
supplementary material.

@@

\noindent\textbf{I. Further Improving Efficiency of HM}

Being able to gain a higher robustness at a lower training cost indiates a
higher efficiency.
%
As discusssed in Sec.~3.1, one potential way to further improve the adversarial
training efficiency is to incorporate adversarial training acceleration methods
such as Free Adversarial Training~\cite{freeat} (for classification) into our
DML adversarial training.
